---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Ashley Ogurek"
output: 
  html_document:
    theme: yeti
    highlight: breezedark
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## I chose this data set because I've always been interested in the environment and ways we has humans can reduce our carbon footprint, so I thought choosing this data set would make this assignment fun and fascinating to me. This data set includes different food categories from each country [Food Consumption and CO2 Emissions](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-02-18/readme.md), as well as their total food consumption and CO2 emissions. 

```{r read-examine-data}
food_consumption <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-18/food_consumption.csv')


```

<br><br>

## Question 1

#### Of beef, pork and poultry, which has the highest CO2 emmissions in the USA?

### Methods
```{r MethodsOne}
food_consumption %>%
  filter(country == "USA") %>%
  filter(food_category == c("Pork", "Poultry", "Beef")) -> team_usa

ggplot(team_usa)+
  aes(x = food_category, y = co2_emmission, fill = food_category)+
  geom_col()+
  labs(y = "CO2 Emmissions", x = "Livestock")+
  scale_fill_discrete(name = "Category")+
  theme_bw()

```

###Answer

It's beef!


<br><br>

## Question 2

#### Which country has the highest beef consumption?

### Methods

```{r MethodsTwo}
food_consumption %>%
  filter(food_category ==  "Beef") %>%
  arrange(-consumption) %>%
  filter(consumption > 30) -> beef_eating

ggplot(beef_eating)+
  aes(y = country, x = consumption, fill = country)+
  geom_col()+
  labs(x = "Consumption", y = "Country") +
  theme(legend.position = "none")

```

### Answer

Argentina.

<br><br>

## Question 3

#### Which country has the highest fish consumption?

### Methods
```{r MethodsThree}
food_consumption %>%
  filter(food_category ==  "Fish") %>%
  arrange(-consumption) %>%
  filter(consumption > 40) -> fish_cons

ggplot(fish_cons)+
  aes(y = country, x = consumption, fill = country)+
  geom_col()+
  labs(x = "Consumption", y = "Country") +
  theme(legend.position = "none")

```

### Answer

Maldives, shockingly  


<br><br>

## Question 4

#### Of beef, lamb & goat, which has the highest CO2 emmissions in Greece?

### Methods
```{r MethodsFour}
food_consumption %>%
  filter(country == "Greece") %>%
  filter(food_category == c("Beef", "Lamb & Goat")) -> team_greece

ggplot(team_greece)+
  aes(x = food_category, y = co2_emmission, fill = food_category)+
  geom_col()+
  labs(y = "CO2 Emmissions", x = "Livestock")+
  scale_fill_discrete(name = "Category")+
  theme_bw()

```

### Answer

Beef again!
