---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: "Ashley Ogurek"
output: 
  html_document:
    theme: yeti
    highlight: breezedark
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## I chose this data set because I've always been interested in the environment and ways we has humans can reduce our carbon footprint, so I thought choosing this data set would make this assignment fun and fascinating to me. This data set includes different food categories from each country [Food Consumption and CO2 Emissions](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-02-18/readme.md), as well as their total food consumption and CO2 emissions. 

```{r read-examine-data}
food_consumption <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-18/food_consumption.csv') #read dataset


```

<br><br>

## Question 1

#### Of beef, pork and poultry, which has the highest CO2 emmissions in the USA?

### Methods
```{r MethodsOne}
food_consumption %>%
  filter(country == "USA") %>% #filtered by country
  filter(food_category == c("Pork",
                            "Poultry",
                            "Beef")) -> team_usa #filtered by food category

ggplot(team_usa)+
  aes(x = food_category, 
      y = co2_emmission, 
      fill = food_category)+ #plotted data with x any y data
  geom_col()+ #created bar graph
  labs(y = "CO2 Emmissions", 
       x = "Livestock")+ #labeled x and y axis
  scale_fill_discrete(name = "Category")+ #changed legend name
  theme_bw() #set theme

```

###Answer

It's beef!


<br><br>

## Question 2

#### Which country has the highest beef consumption?

### Methods

```{r MethodsTwo}
food_consumption %>%
  filter(food_category ==  "Beef") %>% #filtered by food category
  arrange(-consumption) %>% #arranged by highest consumption to lowest
  filter(consumption > 30) -> beef_eating #filtered consumptions only over 30

ggplot(beef_eating)+
  aes(y = country, 
      x = consumption, 
      fill = country)+ #plotted data into x and y axis
  geom_col()+ #created bar graph
  labs(x = "Consumption", 
       y = "Country") + #labeled x and y axis
  theme(legend.position = "none") #removed legend

```

### Answer

Argentina.

<br><br>

## Question 3

#### Which country has the highest fish consumption?

### Methods
```{r MethodsThree}
food_consumption %>%
  filter(food_category ==  "Fish") %>% #filtered by food
  arrange(-consumption) %>% #arranged by highest consumption to lowest
  filter(consumption > 40) -> fish_cons #filtered consumptions only over 40

ggplot(fish_cons)+
  aes(y = country, 
      x = consumption, 
      fill = country)+ #plotted data into x and y axis
  geom_col()+ #created bar graph
  labs(x = "Consumption", 
       y = "Country") + #labeled x and y axis
  theme(legend.position = "none")  #removed legend


```

### Answer

Maldives, shockingly  


<br><br>

## Question 4

#### Of beef, lamb & goat, which has the highest CO2 emmissions in Greece?

### Methods
```{r MethodsFour}
food_consumption %>%
  filter(country == "Greece") %>% #filtered by country
  filter(food_category == c("Beef", 
                            "Lamb & Goat")) -> team_greece #filtered by food

ggplot(team_greece)+
  aes(x = food_category, 
      y = co2_emmission, 
      fill = food_category)+ #inserted data into x and y axis
  geom_col()+ #created bar graph
  labs(y = "CO2 Emmissions", 
       x = "Livestock")+ #labeled x and y axis
  scale_fill_discrete(name = "Category")+ #renamed legend
  theme_bw() #set theme

```

### Answer

Beef again!
